Topological Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-05-15 Paper/paper.tex
minor edits

%
% Single address.
% ---------------
%\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
%\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Christopher J. Tralie}
	{Duke University,  Mathematics\\
	ctralie@alumni.princeton.edu}
  {Matthew Berger}
	{University of Arizona, Computer Science\\
	matthew.sh.berger@gmail.com}
%
\begin{document}
%\ninept
%
\maketitle
%

@@

Our approach to slow motion templates is {\em Eulerian}; that is, we process the video pixel by pixel with no tracking.  Eulerian approaches for video synthesis are attractive due to their simplicity and ease of implementation.  For instance, a Fourier bandpass filter can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.  Additionally, time-domain Eulerian approaches have been used to synthesize infinitely playing stochastic ``video textures''~\cite{schodl2000video}, as well as seamlessly looping video templates from a single cycle of periodic motion ~\cite{Liao2013VideoLoops,Liao2015VideoLoops} (this is not applicable to our problem since we fuse multiple cycles).  There are some pitfalls with Eulerian techniques, however.  They are known to fail for large motions, and also require the user to manually specify frequencies of interest \cite{wu2012eulerian, wadhwa2013phase}.  Furthermore, period-to-period drift due to a moving camera or small motion variations can be problematic, as can unrelated motion in the background or occlusions \cite{stauffer1999adaptive}.

@@

% MSB: opportunity to slim paper by cutting examples 
Many prior works use a combination of sliding window embeddings and TDA, for instance to detect chatter in mechanical systems \cite{khasawneh2016chatter} and quantify periodic activities in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}. However, our approach in using a sliding window jointly with TDA to {\em synthesize} a new result is novel. Related works use spectral geometry to rearrange unstructured collections of images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit} or along a line to order the microscopic images of a developing embryo \cite{dsilva2015diffusionvecordering}. By constrast, we seek a cyclic order, and our input frames are ordered in time, enabling us to construct a sliding window.

>>>>

%
% Single address.
% ---------------
%\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
%\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Christopher J. Tralie}
	{Duke University,  Dept. of Mathematics\\
	ctralie@alumni.princeton.edu}
  {Matthew Berger}
	{University of Arizona, Dept. of Computer Science\\
	matthew.sh.berger@gmail.com}
%
\begin{document}
%\ninept
%
\maketitle
%

@@

Our approach to slow motion templates is {\em Eulerian}; that is, we process the video pixel by pixel with no tracking.  Eulerian approaches for video synthesis are attractive due to their simplicity and ease of implementation.  For instance, a Fourier bandpass filter can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.  Time-domain Eulerian approaches can synthesize infinitely playing stochastic ``video textures''~\cite{schodl2000video}, as well as seamlessly loop video templates from a single cycle of periodic motion ~\cite{Liao2013VideoLoops,Liao2015VideoLoops}, though such approaches are not applicable to our problem since we fuse multiple cycles.  There are some pitfalls with Eulerian techniques, however.  They are known to fail for large motions, and also require the user to manually specify frequencies of interest \cite{wu2012eulerian, wadhwa2013phase}.  Furthermore, period-to-period drift due to a moving camera or small motion variations can be problematic, as can unrelated motion in the background or occlusions \cite{stauffer1999adaptive}.

@@

% MSB: opportunity to slim paper by cutting examples 
Many prior works use a combination of sliding window embeddings and TDA, for instance to detect chatter in mechanical systems \cite{khasawneh2016chatter} and quantify periodic activities in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}. However, our approach in using a sliding window jointly with TDA to {\em synthesize} a new result is novel. Related works use spectral geometry to rearrange unstructured collections of images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit} or along a line to order the microscopic images of a developing embryo \cite{dsilva2015diffusionvecordering}. By constrast, we seek a cyclic reordering given input frames ordered in time, enabling us to construct a sliding window.
